FocalGstar

### 2017-06-15 analysis.Rmd
changed code for generating Focal G* (blur)

### Focal G* (blur)
```{r demo-blur-focalgstar, echo=FALSE, cache=TRUE, fig.width=7, fig.height=4.5}
st <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
for (ws in wsizes) {

@@

  g <- GetisOrd(r, w, st)
  plot_zscore(g,
              title = sprintf("Focal G*: wsize=%d", ws),
              sigma_thresh = 2)
  writeRaster(g,
              sprintf("data/blur/focalgstar-%dx%d-z%02d-w%02d.tif",
                      nrow(r), ncol(r), ZOOMLEVEL, ws),
              overwrite = TRUE)
}
```

>>>>

### Focal G* (blur)

First, we pre-compute the rasters
```{r, echo=FALSE, cache=TRUE}
blur_focalgstar <- list()
pb <- txtProgressBar(max = last(wsizes), style = 3)
st <- GetisOrdLocalStats(r, weight_matrix_circular(FOCAL_MATRIX_SIZE))
for (ws in wsizes) {
  setTxtProgressBar(pb, ws)

@@

  blur_focalgstar[[length(blur_focalgstar) + 1]] <- GetisOrd(r, w, st)
}
close(pb)
```

```{r, eval=FALSE, echo=FALSE}
for (i in seq_along(wsizes)) {
  ws <- wsizes[i]
  g <- blur_focalgstar[[i]]
  writeRaster(g,
              sprintf("data/blur/focalgstar-%03dx%03d-z%02d-w%02d.tif",
                      nrow(g), ncol(g), ZOOMLEVEL, ws),
              overwrite = TRUE)
}
```

```{r raw-blur-focalgstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
op <- par(mar = rep(0, 4))
for (g in blur_focalgstar[RENDERED_IDX]) {
  plot(g, xlab = NA, ylab = NA, legend = FALSE, axes = FALSE, box = FALSE,
       col = COLORMAP, colNA = "black")
}
par(op)
```

```{r demo-blur-focalgstar, echo=FALSE, cache=TRUE, fig.width=6, fig.height=5.5}
for (i in seq_along(wsizes)) {
  ws <- wsizes[i]
  g <- blur_focalgstar[[i]]
  plot_zscore(g,
              title = sprintf("Focal G*: wsize=%d", ws),
              sigma_thresh = 2)
}
```
